Contracts for Contracts

### 2022-11-06 paper.tex
a bit more thoughts

@@

the core model of the language

@@

@@

examining 3-4 cases

>>>>

\paragraph{Contributions}
\begin{itemize}
  \item We propose to add higher-order contracts to programs running on blockchains for
    safer and more reliable smart contracts.
  \item We present a core model that extends the Solidity language with higher-order contracts,
    including its syntax, semantics, and soundness.
  \item We examine a number of real-world cases and shows that our proposed approach
    is effective in ...
  \item We implement our approach on top of the Solidity compiler and shows
    that its runtime overhead is marginal(?) ...
\end{itemize}

@@

the core model of the language (TODO named?)

@@

examining 3-4 cases, they are the proof that the approach works

perhaps also performance evaluation?

@@
